CS222 Project Proposal

### 2019-12-09 proposal/proposal.tex
include an example in formulation and update notation

Our task is to find a subset $\mathcal{D}^* \subset \mathcal{D}$, such that for any class $A_i$, there exists a partition that divides it into some subclasses $S_i^{(l)}$ where $\bigcup_l \{A_{ij} \,|\, (i, j) \in S_i^{(l)}\} = A_i$, and for each subclass $S_i^{(l)}$ there exists a subset of classifiers $D^{(l)} \subseteq \mathcal{D}^*$ where $S_i^{(l)} = \bigcap_d \{I_d \,|\, d \in D^{(l)}\}$.
Here, subclass $S_i^{(l)}$ represents the union of some subsets $A_{ij}$ of class $A_i$, and the union of all subclasses of $A_i$ should reconstruct the $A_i$ itself.
The optimal set of classifiers $\mathcal{D}^*$ should allow us to determine wether a sample belongs to any given subclass $S_i^{(l)}$ using a subset $D^{(l)}$ in it, which in turn determines wether the sample belongs to $A_i$.

There are further constraints and considerations on the optimal set of classifiers $\mathcal{D}^*$.
\begin{itemize}
    \item \textbf{Number of Classifiers.} We need to choose adequate number of classifiers $|\mathcal{D}^*|$ so that it covers all classes. But we prefer to use as less classifiers as possible to save computational consumptions.
    \item \textbf{Network Size.} The size for each classifier is limited. Large networks as classifiers improve accuracy but slow down inferences. Therefore, we will have penalty for large classifiers.
    \item \textbf{Overall Accuracy.} We know the accuracy of each classifier as a prior, but we need to derive the overall accuracy based on it. The $\mathcal{D}^*$ should optimize the overall accuracy along with other goals.
\end{itemize}
These are factors we will consider in the later development and we are open for other suggestions.

>>>>

Our task is to find a subset $D^* \subset \mathcal{D}$, such that for any class $A_i$, there exists a partition that divides it into some subclasses $S_i^{(l)}$ where $A_i = \bigcup_l \{A_{ij} \,|\, (i, j) \in S_i^{(l)}\}$, and for each subclass $S_i^{(l)}$ there exists a subset of classifiers $D^{(l)} \subseteq D^*$ where $S_i^{(l)} = \bigcap_d \{I_d \,|\, d \in D^{(l)}\}$.
Here, subclass $S_i^{(l)}$ represents the union of some subsets $A_{ij}$ of class $A_i$, and the union of all subclasses of $A_i$ should reconstruct the $A_i$ itself.
The optimal set of classifiers $D^*$ should allow us to determine wether a sample belongs to any given subclass $S_i^{(l)}$ using a subset $D^{(l)}$ in it, which in turn determines wether the sample belongs to $A_i$.
Figure~\ref{fig:feasible-example} shows a feasible classifier set $D$ in a simple example.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\linewidth]{fig/formulation_example.png}
    \caption{An Example of Feasible Classifier Set:
    The samples in class $A_1$ is further divided into $A_{11}, A_{12}$ and those in class $A_2$ is further divided into $A_{21}, A_{22}, A_{23}$.
    We do not divide $A_3$ but rename it to $A_{31}$.
    There are 4 discriminators $d_1, d_2, d_3, d_4$ respectively identify $\{A_{11}, A_{12}, A_{21}, A_{22}\}$, $\{A_{21}, A_{31}\}$, $\{A_{22}, A_{23}\}$, and $\{A_{23}, A_{31}\}$.
    We have: \textit{(a)} the intersection of $d_1$ and the compliments of $d_2, d_3$ identifies $A_1 = A_{11} \cup A_{12}$;
    \textit{(b)} the intersection of $d_1$ and $d_2$ identifies $A_{21}$, and its union with $d_3$ determines the entire $A_2$;
    \textit{(c)} the intersection of $d_3$ and the compliment of $d_1$ determines $A_3 = A_{31}$.
    Clearly, $D = \{d_1, d_2, d_3\}$ is a feasible set, where the redundant classifier $d_4$ is not selected.}
    \label{fig:feasible-example}
\end{figure}

There are further constraints and considerations of the optimal set of classifiers $D^*$.
\begin{itemize}
    \item \textbf{Number of Classifiers.} We need to choose adequate number of classifiers $|D^*|$ so that it covers all classes. But we prefer to use as less classifiers as possible to save computational consumptions.
    \item \textbf{Network Size.} The size for each classifier is limited. Large networks as classifiers improve accuracy but slow down inferences. Therefore, we will have penalty for large classifiers.
    \item \textbf{Overall Accuracy.} We know the accuracy of each classifier as a prior, but we need to derive the overall accuracy based on it. The $D^*$ should optimize the overall accuracy along with other goals.
\end{itemize}
These are factors we will consider in the later development and we are open for other suggestions.
